---
title: "2014 Staff Survey"
author: "Andrew Tennikoff, Lily Arasaratnam-Smith"
date: "January 15th, 2015"
output: rmarkdown::tufte_handout
---

--------

# 2014 Staff Survey

\newthought{In keeping with our normal practice,} we present the detailed analysis of this years Alphacrucis Staff Survey.

This document complements the high level overview presentation provided to all staff at the annual staff retreat.
It is intended to go into further detail on each question, expand upon methodologies used and document the assumptions we have made.

As in previous years - and in the spirit of open information, transparency and reproducible research - the quantitative dataset has been made available for further analysis. \marginnote{This copy of the dataset, along with the original version, remain anonymised. The only difference between the two datasets is that we don't include the qualitiative data in this copy, as we feel it has the potential to be \emph{more} identifiable.} We encourage individuals to perform their own analysis, particularly if their assumptions differ from ours, and present their findings to us all. To make this even easier, this PDF has been generated from a document written in *R Markdown* format, allowing the researcher to run all our computations on their own computer, and adjust them as they see fit.


## Objectives of this analysis

\newthought{In presenting the annual staff survey,} our objective is to convey the core themes of the data collected from staff, to staff, in a manner accessible to all staff.

Note that this is not a statement about data accuracy, which it goes without saying should remain as high as possible at all times, but one of the scope of our analysis. There are many areas our analysis could have taken us, but we only persue those within the scope of our brief.

Also, this is not to say that analysis outside this scope is not interesting to us.
We feel this data provides a rich area for exploration, and towards the end of
this document have listed areas we would be personally interested in seeing
our colleagues examine further.

**This remains, however, a primarily _qualitative_ study.** Although we collect quantitative data, its primary use is to categorise the qualitative feedback received. Secondary to this is it's use as a broad, high level overview of the survey to provide a context for the textual analysis to exist in. As such we do not report any summary statistics, such as means, nor compare this data year-on-year. Rather, we simply present the number of reponses for each question within a frequency table, and provide a simple visualisation of this table.

# Methodology: data collection

This survey takes the form of an anonymous, optional survey for all employees
of Alphacrucis College. A link to an online form is emailed to staff in
December, and reponses are collected up until mid Janurary. Within this period
reminder emails are sent to staff in order to maximise the response rate.

This year we received `r  nrow(lkt[(lkt[,2] == 'All staff'),])` responses from
~80 employees. Whilst we don't have employee numbers for corresponding periods in
previous years, this almost certainly represents the highest response rate
received for this survey yet. As our sample size approaches our population size, we become more confident that
our results are representive of AC staff. Of course, this remains a sample and
thus an estimate, so we can not be certain, just less uncertain.

We don't feel that sampling techniques such as stratified or cluster sampling would add
considerably to the representativness of this data, given that our sample
represents close to 75% of the population. However, something that *would*
increase the representativeness of our sample is a test for non-response bias.
We are open to ideas on how best this could be done, whilst maintaining the
annonymity of the survey.


# Methodology: quantative data analysis

Any analysis of quantative data first needs to consider the nature of the data itself in order to draw statistically valid conclusions from it. Stanley Smith Stevens' *Theory of Scales of Measurment*[^sss1946] proposes a heirarchy of four levels:

1. _Nominal data._ Unordered categorical data. (Example: Female, Male)
2. _Ordinal data._ Ordered data, but with no measure of distance (Example: ranking fruit by colour - Very Orange, Orange, Pale Orange)
3. _Interval data._ Ordered data where distance measurment is possible, but where there is no true zero point (Example: temperature measured in Celcius. It doesn't make sense to say 20C is twice as hot as 10C)
4. _Ratio data._ Ordered data with a true zero point, where both distance, and fractions of distance between variables are possible. (Example: absolute tempreture measured in Kelvin.)

Of these categories, the data collected via our Likert questions is of the type *ordinal*. \marginnote{It is of the type ordinal because, whilst we know that Strongly Agree is more positive than Agree, we don't know by how much. Additionally, we don't know that the distance between Strongly Agree and Agree is the same as the distance between Neutral and Disagree.} Most important for this discussion is that __descriptive statistics such as the *mean* and *standard deviation*, or any parametric analysis based on the normal distribution, are invalid parameters for ordinal data.__

Whilst this is relatively uncontroversial in methodological[^blaikie2003] or statistical[^clegg2008] texts, it is somewhat surprising how frequently even published researchers break these rules[^jamieson2004] and treat ordinal data as interval data. Allen and Seaman propose that "an underlying reason for analyzing ordinal data as interval data might be the contention that parametric statistical tests (based on the central limit theorem) are more powerful than nonparametric alternatives. Also, conclusions and interpretations of parametric tests might be considered easier to interpret and provide more information than nonparametric alternatives. However, treating ordinal data as interval (or even ratio) data without examining the values of the dataset and the objectives of the analysis can both mislead and misrepresent the findings of a survey."[^allen2007]

It is our opinion then, that for the data collected via our Likert responses appropriate non-parametric statistical measures for centrality include the mode and median, and for the spread of the distrubutions, the interquartile ranges. Other valid measures may include the use of Kruskall-Wallis models for measures of variance, Chi-Squared and Fisher exact tests for measures for significance, and simple distribution free methods such as tabulations and frequency counts.

Given the earlier statement that ours is primarily a qualitative analysis, we will adopt a conservative approach and restrict our quantitative attention to tabulations and frequency counts. \marginnote{In light of discussions at Staff Retreat we will, however, propose that Fisher's exact test (with the extension to matricies greater than 2x2 offered by Freeman-Halton) provide a statistically rigourous starting point for any analysis into the differences between these two groups. This will be discussed more in the *Areas for further study* section, and we will provide P-values for tests of non-random associations between Academic and Administrative responses in the Appendix as a motivating example.} Where we group responses into Academic and Administrative categories, it is to contextualise discussion about the textual responses, and we do not offer an opinion on whether one group is more- or less-positive than the other. 


# Methodology: Visualisations

The primary method for sumarising our Likert data will be via frequency tables. This will be visualised via use of *diverging stacked bar charts*. Robbins and Heiberger[^robbins2013] provide an excellent discussion on the benefits of this approach in *Design of Diverging Stacked Bar Charts for Likert Scales and Other Applications*.

# Methodology: Thematic analysis

[TODO: LA]



\newpage

# Results: Likert questions

```{r, include=FALSE}
library(xtable)
library(reshape)
library(likert)
# Note: if you're getting likert package errors, it's recommended you install
# the more up to date development version from GitHub
# devtools::install_github('jbryer/likert') 

lkt <- read.csv('Data/2014_likert_qs.csv') # import data
lkt$StartDate <- as.Date(lkt$StartDate, "%Y-%m-%d") # format dates

# Set factors
lkt[c(3:14)] <- lapply(lkt[c(3:14)], factor, levels=c(
  "Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"),
  labels=c('SD', 'D', 'N', 'A', 'SA'))
lkt[2]  <- lapply(lkt[2], factor, levels=c("Academia", "Administration"))

# Add copy of data regrouped as "All staff" to ease ploting
lkt_2 <- lkt
lkt_2[,2] <- factor("All staff")
lkt <- rbind(lkt, lkt_2)
lkt[,2] <- ordered(lkt[,2], levels=c("All staff", "Academia", "Administration")) # Reorder levels

# Rename cols
colnames(lkt) <- c(
  "StartDate",
  "Do you work within Academia or Administration?",
  "I think AC staff meetings are run well",
  "I enjoy AC staff camps",
  "AC graduation and other public events are run well",
  "I feel valued by my manager for the work I do",
  "I feel valued by my peers for the work I do",
  "I feel I have the skills to do the job I've been asked to do",
  "I have a clear understanding of the AC organisational structure",
  "I feel I fit into the organisational culture of AC",
  "I attend Chapel because I want to, not because I have to",
  "The mission and vision of the College has been clearly communicated to me",
  "I consider my office area and staff facilities adequate in order to perform my duties",
  "I am likely to recommend AC as an employer of choice")

# Set xtable options
options(xtable.comment = FALSE)
options(xtable.booktabs = TRUE)
```

\newthought{With the caveats mentioned above in mind,} we present a brief high level overview of the data in order to provide a context for the qualitative analysis in the next section. In these initial sections we will also print the R commands used to generate the data for the purposes of transparency. As mentioned earlier, the R commands for this whole report can be seen in the  associated *R Markdown* file used to generate this PDF.

```{r, fig.height=8, fig.width=10, fig.fullwidth=TRUE, fig.caption="Normalised frequency counts for all responses, ordered from the highest number of Agree/Strongly Agree responses to the least. Includes response rates (n) for each question."}
all_staff <- lkt[,2] == "All staff"
plot(likert(lkt[all_staff, 3:14]), text.size=4, plot.percent.neutral=FALSE,
     include.histogram = TRUE, wrap=30)
```

As can be seen in the right hand column, the response rates for each question remain $\ge$ 55 as indicated in grey, with the number of people not providing an answer indicated in red. \marginnote{Presumably the higher non-response rate for "I enjoy AC staff camps" is due to the number of new staff hired over the year who had not yet attended a staff camp.}

We are primarily interested in the number of people who either agree with the statement (ie. Agree, or Strongly Agree), or disagree with the statement (ie. Disagree, or Strongly Disagree). This is indicated by the percentage figures to the left and right of the bars. We do not include percentages for neutral responses, but these can be computed by simply subtracting the displayed percentages from 100%.

How these responses break down into Agree/Strongly Agree and Disagree/Strongly Disagree is displayed in the bar chart, but is of less interest to us in this report.

--------

For this next plot we have overlayed the responses received for each question in an attempt to get a
broad sense of the overall sentiment of respondents.

```{r, fig.height=8, fig.width=10, fig.fullwidth=TRUE, fig.caption="TO DO"}
all_staff <- lkt[,2] == "All staff"
plot(likert(lkt[all_staff, 3:14]), type='density', facet=FALSE) + theme(legend.position='none')
```

We recommend against reading too much into this plot, and suggest that its primary usefullness is
as an initial step in exploring the data.

The primary limitations of this plot stem from the
assumptions the plot makes. In order to plot discrete data points on a
continuous scale, we need to interpolate between data points.
We achieve this via a KDE, \marginnote{KDE: Kernal Density Estimator} which requires parrameters such as the
smoothing kernel to be used (_gaussian_ in our case), and the amount of smoothing bandwidth, or
standard deviation, to use to scale the smoothing kernel[^sheather1991]. This, however, violates our
above statement that standard deviations should not be computed for ordinal data. In effect,
to create this plot we have had to make the assumption that the distance between each possible response
is uniform.

Plotting grouped bar charts of responses to each question would be a more accurate
representation of the data, but this would require positioning the questions next to each
other rather than overlaying them. This would be very difficult to interprete visually.


\newpage

## Question 1: I think AC staff meetings are run well

For this first question we will *show our working* by displaying the underlying R commands used to create the summary table and plot. The commands only differ slightly between questions, so in the interests of brevity we will only present the results for the remaining questions.

Frequency table of responses to the first question, grouped by staff type:

```{r, results='asis'}
q3_summary <- table(lkt[,2], lkt[,3]) # Create frequency counts for q3 grouped by staff type
q3_summary <- addmargins(q3_summary, margin=2) # Add in row totals
xtable(q3_summary, digits=0,
       caption='Frequency table for \"I think staff meetings are run well\"')
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I think AC staff meetings are run well\""}
q3_lkt <- likert(lkt[3], grouping = lkt[,2]) # Group q3 responses by staff type
plot(q3_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Well spaced out, good amount of info communicated,
                           chance for connecting & reflecting
 
                 Disagree  Boring, lack of opportunities to ask questions of
                           leadership, repetitive info

 Administration  Agree     Informative, fun, good to align goals, good to hear
                           departmental updates
 
                 Disagree  One-way communication, staff input is not solicited
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.


\newpage

## Question 2: I enjoy AC staff camps

Frequency table of responses to the first question, grouped by staff type:

```{r, results='asis', echo=FALSE}
q <- 4
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I enjoy AC staff camps\"", echo=FALSE}
q <- 4
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Opportunity to regenerate sense of community, good
                           speakers, chance to meet staff you don’t usually
                           meet, preparation for the year together
 
                 Disagree  N/A (No one disagreed!)

 Administration  Agree     Aligning of goals/vision, team bonding without
                           distractions, inspirational, well-run, off-site is
                           enjoyable
 
                 Disagree  Too much of self-cheering
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 3: AC graduation and other public events are run well

```{r, results='asis', echo=FALSE}
q <- 5
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"AC graduation and other public events are run well\"", echo=FALSE}
q <- 5
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Gets better each year, professional yet warm &
                           inviting, improvements reflects growing confidence
                           in our academic standing
 
                 Disagree  (No qualitative response provided)

 Administration  Agree     Community-minded, clear info, great vibe from students, staff & visitors
 
                 Disagree  Staff being asked to volunteer without pay
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 4: I feel valued by my manager for the work I do

```{r, results='asis', echo=FALSE}
q <- 6
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I feel valued by my manager for the work I do\"", echo=FALSE}
q <- 6
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Good communication, positive feedback
 
                 Disagree  (No qualitative response provided)

 Administration  Agree     Respect, verbal appreciation, feedback, autonomy, affirmation, trust/confidence given, approachability, ownership of tasks
 
                 Disagree  No recognition of extra work done, lack of feedback/affirmation, pay doesn’t reflect value
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 5: I feel valued by my peers for the work I do

```{r, results='asis', echo=FALSE}
q <- 7
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I feel valued by my peers for the work I do\"", echo=FALSE}
q <- 7
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Good camaraderie, team feeling & empathy
 
                 Disagree  N/A (No one disagreed!)

 Administration  Agree     (Peers) generous, helpful, take time to socialise, provide encouragement/affirmation
 
                 Disagree  (Peers) don’t understand the work done by me; make decisions that make my work harder without consulting me
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 6: I feel I have the skills to do the job I've been asked to do

```{r, results='asis', echo=FALSE}
q <- 8
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I feel I have the skills to do the job I've been asked to do\"", echo=FALSE}
q <- 8
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Yes, but always something new to learn
 
                 Disagree  N/A (No one disagreed!)

 Administration  Agree     “Jobs are getting done,” “I’m just good!”
 
                 Disagree  Role unclear; feel out of my depth
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 7: I have a clear understanding of the AC organisational structure

```{r, results='asis', echo=FALSE}
q <- 9
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I have a clear understanding of the AC organisational structure\"", echo=FALSE}
q <- 9
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

No qualitative response was asked for this question.


\newpage

## Question 8: I feel I fit into the organisational culture of AC

```{r, results='asis', echo=FALSE}
q <- 10
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I feel I fit into the organisational culture of AC\"", echo=FALSE}
q <- 10
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Understand the aims of the organisations, teamwork, culture, vision, “time for tea”, pioneering
 
                 Disagree  N/A (No one disagreed!)

 Administration  Agree     Christian/Pentecostal values, sense of being part of bigger purpose, sense of belonging
 
                 Disagree  Feel excluded by decisions made without consultation
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 9: I attend Chapel because I want to, not because I have to

```{r, results='asis', echo=FALSE}
q <- 11
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I attend Chapel because I want to, not because I have to\"", echo=FALSE}
q <- 11
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Most times, but not always
 
                 Disagree  Frustrating when speakers contradict what we teach, compulsory chapel is contradiction of Christian freedom

 Administration  Agree     Worship, fellowship, community
 
                 Disagree  (No qualitative response provided)
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 10: The mission and vision of the College has been clearly communicated to me

```{r, results='asis', echo=FALSE}
q <- 12
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"The mission and vision of the College has been clearly communicated to me\"", echo=FALSE}
q <- 12
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

No qualitative response was asked for this question.


\newpage

## Question 12: I consider my office area and staff facilities adequate in order to perform my duties

```{r, results='asis', echo=FALSE}
q <- 13
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I consider my office area and staff facilities adequate in order to perform my duties\"", echo=FALSE}
q <- 13
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Having an office makes job easier
 
                 Disagree  Cubicles not conducive for the type of work (e.g. Marking)

 Administration  Agree     Safe, clean, good IT support 
 
                 Disagree  Cramped, cubicle not conducive for creative work, noise, lack of privacy for confidential phone conversations
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

## Question 13: I am likely to recommend AC as an employer of choice

```{r, results='asis', echo=FALSE}
q <- 14
q_summary <- table(lkt[,2], lkt[,q]) # Create frequency counts for q grouped by staff type
q_summary <- addmargins(q_summary, margin=2) # Add in row totals
xtable(q_summary, digits=0,
       caption=paste('Frequency table for \"', names(lkt[q]), '\"', sep='') )
```

Corresponding visualisation of the proportional frequency count, grouped by staff type:

```{r, fig.height=2.5, fig.width=9, fig.cap = "Frequency table visualisation for \"I am likely to recommend AC as an employer of choice\"", echo=FALSE}
q <- 14
q_lkt <- likert(lkt[q], grouping = lkt[,2]) # Group q responses by staff type
plot(q_lkt, text.size=4, include.histogram=TRUE, plot.percent.neutral=FALSE,
     group.order=c('All staff', 'Academia', 'Administration'))
```

-------------------------------------------------------------------------------
  Who             What     Why
---------------  --------  ----------------------------------------------------
 Academia        Agree     Encouraging culture, good ethos
 
                 Disagree  Salary

 Administration  Agree     Good people, environment, vision, recognition of skills
 
                 Disagree  Lack of long-term career management; low salary
-------------------------------------------------------------------------------

Table: Thematic annalysis of qualitative responses, grouped by staff type and response type.

\newpage

# Results: Other quantative questions


\newpage

# Results: Open response questions

## Assuming your current salary remains the same, what other factors would enhance your job satisfaction?

\newthought{There were some common themes} reported by both Academic and Administrative staff for this question. These can be summarised as follows:

-------------------------------------------------------------------------------
Academia                                      Administration
--------------------------------------------  ---------------------------------
Bonuses                                       Bonuses

Flexibility in time/location                  Freedom with time management

Regular/positive feedback from manager        Regular/positive feedback from manager

Autonomy                                      Autonomy
-------------------------------------------------------------------------------

Table: Common themes expressed by Academic and Administrative staff.


Other items identified by __Academia__ include the following:

- Ongoing training
- Understanding and value of academic expertise
- Team lunches/activities
- Effective marketing
- Better faculty support
- Organisational culture supportive of freedom of choice
- More incentives to do well


Other items identified by __Administration__ include the following:

- Promotion opportunities
- More staff to share workload
- Indoor plants 
- Pastoral care
- Clearer job parameters 
- Not being forced to take annual leave during Christmas break 
- Small rewards


\newpage

## What causes you frustration in your specific role at AC?

\newthought{Common themes expressed} by all staff inlcude: (i) workload, (ii) being
given responsibility without authority, and (iii) (lack of) resources.

Other, less thematic frustrations identified by __Academia__ include the following:

- Work overload
- Non-engaging students
- Poor or delayed communication
- Isolation between campuses
- Compliance
- Workload calculator isn’t comprehensive
- Seeing good people leave
- Lack of accountability/management
- Being given responsibility without authority
- Criticism/miscommunication
- Inefficiencies in other departments
- Inconsistencies between organisational values and behaviour
- Lack of uninterrupted time
- Lack of time/resources for research

Other, less thematic frustrations identified by __Administration__ include the following:

- Less opportunities for upward promotion
- Lack of time for prayer
- Lack of interest in listening to suggestions for improvement
- Increased workload due to others’ interference
- Lack of clear KPIs
- Lack of authority to make decisions that affect one’s role
- Lack of consistency in the way people/churches are treated (i.e. some given special treatment)
- Inconsistencies in staff commitment to college
- Unenforced rules (for students)
- Lack of resources
- Lack of vision and strategic planning
- Allocation of tasks without information needed to complete them
- Sudden heavy increase in workload without warning
- Staff not communicating their whereabouts


\newpage

## What are the top three things you enjoy about your specific role at AC?

\newthought{The top three things enjoyed} by both Academic and Administrative staff
shared a high degree of similarity. In no particular order they are as follows:

-------------------------------------------------------------------------------
Academia                                      Administration
--------------------------------------------  ---------------------------------
People                                        People

Purpose                                       Purpose

Variety/challenges                            Environment (facilities, support, team, etc.)
-------------------------------------------------------------------------------

Table: Top three things enjoyed by Academia and Administration.


\newpage


## Identify three reasons why you choose to work at AC?

\newthought{Likewise, there was a large degree of similarity} between Academia and
Administration when asked to identify reasons for continuing to choose to work at AC.

-------------------------------------------------------------------------------
Academia                                      Administration
--------------------------------------------  ---------------------------------
Christian/Pentecostal ethos                   Christian environment

Sense of calling                              College’s vision

Job fit (sense of contribution,               Environment (support, opportunities,
match with skills, etc.)                      contribution, etc.)
-------------------------------------------------------------------------------

Table: Main reasons Academic and Administrative staff choose to work at AC.


\newpage

# Summary

[TODO]



\newpage

# Areas for further study

- Time series
- Independence of Academic and Administrative responses
- Correlations
- Time of response predictive of sentiment


\newpage

# Appendix 1: 


[^sss1946]: S. S. Stevens, *Science.* 7 June 1946: **103** (2684), 677-680.
[^blaikie2003]: Blaikie N. *Analysing Quantitative Data.* London: Sage Publications 2003.
[^clegg2008]: Clegg F. *Simple Statistics.* Cambridge: Cambridge University Press 1998.
[^jamieson2004]: Jamieson, Susan. "Likert scales: how to (ab) use them." *Medical education* 38.12 (2004): 1217-1218.
[^allen2007]: Allen, I. Elaine, and Christopher A. Seaman. "Likert scales and data analyses." *Quality Progress* 40.7 (2007): 64-65.
[^robbins2013]: Heiberger, Richard M., and Naomi B. Robbins. "Design of Diverging Stacked Bar Charts for Likert Scales and Other Applications." *Journal of Statistical Software* submitted (2013): 1-36.
[^sheather1991]: Sheather, S. J. and Jones M. C. (1991) A reliable data-based bandwidth selection method for kernel density estimation. *J. Roy. Statist. Soc.* B, 683–690.