---
title: 'AC Staff Survey: 2014'
author: "Andrew Tennikoff & Lily Arasaratnam-Smith"
date: "16 January 2015"
output:
  ioslides_presentation:
    fig.width: 7
    incremental: yes
    keep_md: yes
    transition: faster
    widescreen: yes
runtime: shiny
---

# Overview

## Overview: About the survey

``` {r, include=FALSE}
library('likert')
library('devtools')

# Ideally use setwd(), but causes shinyapps.io problems
# setwd('/Users/andrew/Documents/Code/R projects/2014 Staff Survey')

# So... try to use source('some url'), but R can't read http*s* :-|
# source('https://gist.github.com/atenni/2b859da145b6f99aa8b8')

# So... use devtools::source_gist
source_gist(id='https://gist.github.com/atenni/2b859da145b6f99aa8b8')
```

- **Total number of respondents:** `r sum(table(clean_data[2]))`
- **Academic responses:** `r table(clean_data[2])[1]`
- **Administration responses:** `r table(clean_data[2])[2]`
- **Average time to complete:** [TODO]
- **Total questions:** 20
- **Total questions including "If… why?" questions:** 44 (!)

## Overview: New… and Improved!

- New questions:
    - Chapel
    - Deeper dive on communication
    - Simple job satisfaction enhancements
- Improved questions:
    - But… _why?_
    - Fix ambiguities ("management")
    - Remove questions better suited to other forums ("level of job training on
      commencement")

## 

## ~Overview: Year on year

- 20 questions
- 46 responses: (Academia: 20, Administration: 26)

## ~Tangent: Thoughts on Likert-scale visualisations

- Pros:
    - Common
    - Easy to understand
    - Easy to compare

## ~Tangent: Thoughts on Likert-scale visualisations

- Cons:
    - Assumes uniform scale
    - Summary statistics with small sample sizes
    - While the _mean_ (first statistical moment) describes the bulk of the
      data, later moments such as _variance_ and _skewness_ contain important
      infomation too
    - (…but while we all understand what an average is, not everyone will be
      familar with _variance_, _skewness_, _kurtosis_, etc.)

## Solution: Don't summarise { .smaller }

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
# knitr::kable(summary(l, ordered=FALSE))
h3(names(clean_data[3]))
table(clean_data[3])
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
plot(l)
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)], grouping=clean_data[[2]])
plot(l)
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
plot(l, type='heat')
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)], grouping=clean_data[[2]])
plot(l, type='density')
```

## 2014's responses [TODO: Year on year.]

```{r, echo=FALSE}
fluidPage(
  verticalLayout(
    selectInput("q_select",
                label = "Question:",
                choices = setNames(c(3:13, 22), names(clean_data[c(3:13, 22)])),
                selectize=TRUE,
                width='100%')
    ),
    
    renderPlot({
      q_num <- as.numeric(input$q_select)
      q <- likert(clean_data[q_num])
      q_title <- names(clean_data[q_num])  
      
      plot(q, wrap=20) + ggtitle(q_title) + theme(axis.text=element_text(size=12))
    }, height=200, width=940)
)
```

## 2014: Academia vs Administration














## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```
