---
title: 'AC Staff Survey: 2014'
author: "Andrew Tennikoff & Lily Arasaratnam-Smith"
date: "16 January 2015"
output:
  ioslides_presentation:
    fig.width: 7
    incremental: yes
    keep_md: yes
    transition: faster
    widescreen: yes
runtime: shiny
---

# Overview

## Overview: About the survey

``` {r, include=FALSE}
#library('likert')
#library('devtools')

# Ideally use setwd(), but causes shinyapps.io problems
# setwd('/Users/andrew/Documents/Code/R projects/2014 Staff Survey')

# So... try to use source('some url'), but R can't read http*s* :-|
# source('https://gist.github.com/atenni/2b859da145b6f99aa8b8')

# So... use devtools::source_gist
# devtools::source_gist(id='https://gist.github.com/atenni/2b859da145b6f99aa8b8')

# But Windows sucks and has 
# So use `eval`
# library(RCurl)
#   eval( expr = 
#     parse(text=getURL("https://gist.githubusercontent.com/atenni/2b859da145b6f99aa8b8/raw/74701697d00556dc96ba0471b0189eea0dd2a51f/2014%20Staff%20Survey%20data%20cleanup.R",
#           ssl.verifypeer=FALSE,
#           cainfo="C:\\Users\\atennikoff\\Documents\\R\\win-library\\3.1\\RCurl\\CurlSSL\\ca-bundle.crt") ))

# Windows...
# source('2014 Staff Survey data cleanup.R')

library('likert')
library('RCurl')
library('reshape')

# Windows...
#d <- getURL('https://gist.githubusercontent.com/atenni/39d8de95dfbae4d21cfc/raw/7177ccae1aa32c4489fd69ab433539c9b247f142/AC%202014%20Staff%20Survey.csv')
#data <- read.csv(text=d)

data <- read.csv('~/GitHub/ss2014/Sheet_1.csv')

# Drop extra SurveyMonkey row
data <- data[-1,]

colnames(data) <- c(
  "RespondentID",
  "CollectorID",
  "StartDate",
  "EndDate",
  "IP Address",
  "Email Address",
  "First Name",
  "LastName",
  "Custom Data",
  "Do you work within Academia or Administration?",
  "I think AC staff meetings are run well",
  "Feedback: I think AC staff meetings are run well",
  "I enjoy AC staff camps",
  "Feedback: I enjoy AC staff camps",
  "AC graduation and other public events are run well",
  "Feedback: AC graduation and other public events are run well",
  "I feel valued by my manager for the work I do",
  "Feedback: I feel valued by my manager for the work I do",
  "I feel valued by my peers for the work I do",
  "Feedback: I feel valued by my peers for the work I do",
  "I feel I have the skills to do the job I've been asked to do",
  "Feedback: I feel I have the skills to do the job I've been asked to do",
  "I have a clear understanding of the AC organisational structure",
  "I feel I fit into the organisational culture of AC",
  "Feedback: I feel I fit into the organisational culture of AC",
  "I attend Chapel because I want to, not because I have to",
  "Feedback: I attend Chapel because I want to, not because I have to",
  "The mission and vision of the College has been clearly communicated to me",
  "I consider my office area and staff facilities adequate in order to perform my duties",
  "Feedback: I consider my office area and staff facilities adequate in order to perform my duties",
  "How do you feel about: Alphacrucis (the organisation) now?",
  "Feedback: How do you feel about: Alphacrucis (the organisation) now?",
  "How do you feel about: Alphacrucis (the organisation) 2 years from now?",
  "Feedback: How do you feel about: Alphacrucis (the organisation) 2 years from now?",
  "How do you feel about: Working conditions at Alphacrucis now?",
  "Feedback: How do you feel about: Working conditions at Alphacrucis now?",
  "How do you feel about: Working conditions at Alphacrucis 2 years from now?",
  "Feedback: How do you feel about: Working conditions at Alphacrucis 2 years from now?",
  "How do you feel about communication between: You and your peers within your department?",
  "Feedback: How do you feel about communication between: You and your peers within your department?",
  "How do you feel about communication between: You and other departments?",
  "Feedback: How do you feel about communication between: You and other departments?",
  "How do you feel about communication between: You and your manager?",
  "Feedback: How do you feel about communication between: You and your manager?",
  "How do you feel about communication between: You and your direct reports (if appropriate)?",
  "Feedback: How do you feel about communication between: You and your direct reports (if appropriate)?",
  "I am likely to recommend AC as an employer of choice",
  "Feedback: I am likely to recommend AC as an employer of choice",
  "Assuming your current role and salary remain the same, what other factors would enhance your job satisfaction?",
  "What causes you frustration in your specific role at AC?",
  "What are the top three things you enjoy about your specific role at AC?",
  "Identify three reasons why you choose to work at AC",
  "Do you have any further comments on your employment experience at AC?")

## CLEAN UP DATA ##
# Select only quantitive data
unnecessary_vars <- c(-1, -2, -4:-9, seq(-12, -22, -2), -25, -27,
                      seq(-30,-46, -2), -48:-53)
clean_data <- data[unnecessary_vars]

# Format dates
clean_data$StartDate <- as.Date(clean_data$StartDate, "%m/%d/%Y %H:%M:%S")

# Create factors
likert_vars <- c(3:13, 22)
likert_labels <-c("Strongly Disagree", "Disagree", "Neutral", "Agree",
                  "Strongly Agree")
clean_data[likert_vars] <- lapply(clean_data[likert_vars], factor, levels=1:5,
                                  labels=likert_labels)
clean_data[2] <- lapply(clean_data[2], factor, levels=1:2,
                        labels=c('Academia', 'Administration'))

## CREATE LIKERT QUESTIONS ##
ss2014_combined <- likert(clean_data[c(3:13, 22)])
ss2014_split <- likert(clean_data[c(3:13, 22)], grouping=clean_data[[2]])


```

- **Total number of respondents:** `r sum(table(clean_data[2]))`
- **Academic responses:** `r table(clean_data[2])[1]`
- **Administration responses:** `r table(clean_data[2])[2]`
- **Average time to complete:** [TODO]
- **Total questions:** 20
- **Total questions including "If… why?" questions:** 44 (!)

## Overview: New… and Improved!

- New questions:
    - Chapel
    - Deeper dive on communication
    - Simple job satisfaction enhancements
- Improved questions:
    - But… _why?_
    - Fix ambiguities ("management")
    - Remove questions better suited to other forums ("level of job training on
      commencement")

## 

## ~Overview: Year on year

- 20 questions
- 46 responses: (Academia: 20, Administration: 26)

## ~Tangent: Thoughts on Likert-scale visualisations

- Pros:
    - Common
    - Easy to understand
    - Easy to compare

## ~Tangent: Thoughts on Likert-scale visualisations

- Cons:
    - Assumes uniform scale
    - Summary statistics with small sample sizes
    - While the _mean_ (first statistical moment) describes the bulk of the
      data, later moments such as _variance_ and _skewness_ contain important
      infomation too
    - (…but while we all understand what an average is, not everyone will be
      familar with _variance_, _skewness_, _kurtosis_, etc.)

## Solution: Don't summarise { .smaller }

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
# knitr::kable(summary(l, ordered=FALSE))
h3(names(clean_data[3]))
table(clean_data[3])
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
plot(l)
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)], grouping=clean_data[[2]])
plot(l)
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)])
plot(l, type='heat')
```

## Solution: Don't summarise

```{r, echo=FALSE}
l <- likert(clean_data[c(3:7)], grouping=clean_data[[2]])
plot(l, type='density')
```

## 2014's responses [TODO: Year on year.]

```{r, echo=FALSE}
fluidPage(
  verticalLayout(
    selectInput("q_select",
                label = "Question:",
                choices = setNames(c(3:13, 22), names(clean_data[c(3:13, 22)])),
                selectize=TRUE,
                width='100%')
    ),
    
    renderPlot({
      q_num <- as.numeric(input$q_select)
      q <- likert(clean_data[q_num])
      q_title <- names(clean_data[q_num])  
      
      plot(q, wrap=20) + ggtitle(q_title) + theme(axis.text=element_text(size=12))
    }, height=200, width=940)
)
```

## 2014: Academia vs Administration














## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```
